Supplementary Materials

### 2024-05-28 supplementary_materials/supplementary_materials.Rmd
post-hoc sensitivty

```{r bacsens}
#| fig.cap: "Plot of intercept estimates from sensitivity analysis for the FIB regression model. Individual points are the intercept estimates with 95% confince intervals for the regression model fit leaving out the study value indicated on the y-axis. The vertical solid line and dotted lines indicate the intercept and 95% confidence intervals for the model that includes all values. Any study values outside of the full model confidence intervals would be considered and outlier."
#| fig.height: 8
#| fig.width: 8
#| out.width: "100%"
tar_read(bac_sens, store = store)$p1
```

```{r tnsens}
#| fig.cap: "Plot of intercept estimates from sensitivity analysis for the TN regression model. Individual points are the intercept estimates with 95% confince intervals for the regression model fit leaving out the study value indicated on the y-axis. The vertical solid line and dotted lines indicate the intercept and 95% confidence intervals for the model that includes all values. Any study values outside of the full model confidence intervals would be considered and outlier."
#| fig.height: 5.5
#| fig.width: 8
#| out.width: "100%"
tar_read(tn_sens, store = store)$p1
```

```{r dinsens}
#| fig.cap: "Plot of intercept estimates from sensitivity analysis for the DIN regression model. Individual points are the intercept estimates with 95% confince intervals for the regression model fit leaving out the study value indicated on the y-axis. The vertical solid line and dotted lines indicate the intercept and 95% confidence intervals for the model that includes all values. Any study values outside of the full model confidence intervals would be considered and outlier."
#| fig.height: 7
#| fig.width: 8
#| out.width: "100%"
tar_read(tin_sens, store = store)$p1
```

```{r tpsens}
#| fig.cap: "Plot of intercept estimates from sensitivity analysis for the TP regression model. Individual points are the intercept estimates with 95% confince intervals for the regression model fit leaving out the study value indicated on the y-axis. The vertical solid line and dotted lines indicate the intercept and 95% confidence intervals for the model that includes all values. Any study values outside of the full model confidence intervals would be considered and outlier."
#| fig.height: 5.5
#| fig.width: 8
#| out.width: "100%"
tar_read(tp_sens, store = store)$p1
```

```{r po4sens}
#| fig.cap: "Plot of intercept estimates from sensitivity analysis for the PO\\textsubscript{4} regression model. Individual points are the intercept estimates with 95% confince intervals for the regression model fit leaving out the study value indicated on the y-axis. The vertical solid line and dotted lines indicate the intercept and 95% confidence intervals for the model that includes all values. Any study values outside of the full model confidence intervals would be considered and outlier."
#| fig.height: 4
#| fig.width: 8
#| out.width: "100%"
tar_read(po4_sens, store = store)$p1
```

```{r tsssens}
#| fig.cap: "Plot of intercept estimates from sensitivity analysis for the TSS regression model. Individual points are the intercept estimates with 95% confince intervals for the regression model fit leaving out the study value indicated on the y-axis. The vertical solid line and dotted lines indicate the intercept and 95% confidence intervals for the model that includes all values. Any study values outside of the full model confidence intervals would be considered and outlier."
#| fig.height: 4.5
#| fig.width: 8
#| out.width: "100%"
tar_read(tss_sens, store = store)$p1
```

@@

>>>>

```{r bacsens}
#| fig.cap: "Plot of intercept estimates from sensitivity analysis for the FIB regression model. Individual points are the intercept estimates with 95% confince intervals for the regression model fit leaving out the study value indicated on the y-axis. The vertical solid line and dotted lines indicate the intercept and 95% confidence intervals for the model that includes all values. Any intercept estimates outside of the full model confidence intervals implies the excluded study is a potential outlier."
#| fig.height: 8
#| fig.width: 8
#| out.width: "100%"
tar_read(bac_sens, store = store)$p1
```

```{r tnsens}
#| fig.cap: "Plot of intercept estimates from sensitivity analysis for the TN regression model. Individual points are the intercept estimates with 95% confince intervals for the regression model fit leaving out the study value indicated on the y-axis. The vertical solid line and dotted lines indicate the intercept and 95% confidence intervals for the model that includes all values. Any intercept estimates outside of the full model confidence intervals implies the excluded study is a potential outlier."
#| fig.height: 5.5
#| fig.width: 8
#| out.width: "100%"
tar_read(tn_sens, store = store)$p1
```

```{r dinsens}
#| fig.cap: "Plot of intercept estimates from sensitivity analysis for the DIN regression model. Individual points are the intercept estimates with 95% confince intervals for the regression model fit leaving out the study value indicated on the y-axis. The vertical solid line and dotted lines indicate the intercept and 95% confidence intervals for the model that includes all values. Any intercept estimates outside of the full model confidence intervals implies the excluded study is a potential outlier."
#| fig.height: 7
#| fig.width: 8
#| out.width: "100%"
tar_read(tin_sens, store = store)$p1
```

```{r tpsens}
#| fig.cap: "Plot of intercept estimates from sensitivity analysis for the TP regression model. Individual points are the intercept estimates with 95% confince intervals for the regression model fit leaving out the study value indicated on the y-axis. The vertical solid line and dotted lines indicate the intercept and 95% confidence intervals for the model that includes all values. Any intercept estimates outside of the full model confidence intervals implies the excluded study is a potential outlier."
#| fig.height: 5.5
#| fig.width: 8
#| out.width: "100%"
tar_read(tp_sens, store = store)$p1
```

```{r po4sens}
#| fig.cap: "Plot of intercept estimates from sensitivity analysis for the PO\\textsubscript{4} regression model. Individual points are the intercept estimates with 95% confince intervals for the regression model fit leaving out the study value indicated on the y-axis. The vertical solid line and dotted lines indicate the intercept and 95% confidence intervals for the model that includes all values. Any intercept estimates outside of the full model confidence intervals implies the excluded study is a potential outlier."
#| fig.height: 4
#| fig.width: 8
#| out.width: "100%"
tar_read(po4_sens, store = store)$p1
```

```{r tsssens}
#| fig.cap: "Plot of intercept estimates from sensitivity analysis for the TSS regression model. Individual points are the intercept estimates with 95% confince intervals for the regression model fit leaving out the study value indicated on the y-axis. The vertical solid line and dotted lines indicate the intercept and 95% confidence intervals for the model that includes all values. Any intercept estimates outside of the full model confidence intervals implies the excluded study is a potential outlier."
#| fig.height: 4.5
#| fig.width: 8
#| out.width: "100%"
tar_read(tss_sens, store = store)$p1
```

@@

```{r bacsource}
#| fig.cap: "Post-hoc sensitivty analysis of fecal indicator bacteria models to exclusion of agriculture or urban runoff sources. The vertical solid line and dotted lines indicate the intercept and 95% confidence intervals for the model that includes all values. Any intercept estimates outside of the full model confidence intervals implies the excluded sources are overly influential."
#| fig.height: 3
#| fig.width: 8 
#| out.width: "100%"
 tar_read(bac_source, store = store)$p1
```

```{r tnsource}
#| fig.cap: "Post-hoc sensitivty analysis of total nitrogen models to exclusion of agriculture or urban runoff sources. The vertical solid line and dotted lines indicate the intercept and 95% confidence intervals for the model that includes all values. Any intercept estimates outside of the full model confidence intervals implies the excluded sources are overly influential."
#| fig.height: 3
#| fig.width: 8
#| out.width: "100%"
 tar_read(tn_source, store = store)$p1
```

```{r dinsource}
#| fig.cap: "Post-hoc sensitivty analysis of dissolved inorganic nitrogen models to exclusion of agriculture or urban runoff sources. The vertical solid line and dotted lines indicate the intercept and 95% confidence intervals for the model that includes all values. Any intercept estimates outside of the full model confidence intervals implies the excluded sources are overly influential."
#| fig.height: 3
#| fig.width: 8
#| out.width: "100%"
 tar_read(tin_source, store = store)$p1
```

```{r tpsource}
#| fig.cap: "Post-hoc sensitivty analysis of total phosphorus models to exclusion of agriculture or urban runoff sources. The vertical solid line and dotted lines indicate the intercept and 95% confidence intervals for the model that includes all values. Any intercept estimates outside of the full model confidence intervals implies the excluded sources are overly influential."
#| fig.height: 3
#| fig.width: 8 
#| out.width: "100%"
 tar_read(tp_source, store = store)$p1
```

```{r po4source}
#| fig.cap: "Post-hoc sensitivty analysis of orthophosphate models to exclusion of agriculture or urban runoff sources. The vertical solid line and dotted lines indicate the intercept and 95% confidence intervals for the model that includes all values. Any intercept estimates outside of the full model confidence intervals implies the excluded sources are overly influential."
#| fig.height: 3
#| fig.width: 8
#| out.width: "100%"
 tar_read(po4_source, store = store)$p1
```

```{r tsssource}
#| fig.cap: "Post-hoc sensitivty analysis of total suspended sediment models to exclusion of agriculture or urban runoff sources. The vertical solid line and dotted lines indicate the intercept and 95% confidence intervals for the model that includes all values. Any intercept estimates outside of the full model confidence intervals implies the excluded sources are overly influential."
#| fig.height: 3
#| fig.width: 8
#| out.width: "100%"
 tar_read(tss_source, store = store)$p1
```

```{r bacscale}
#| fig.cap: "Post-hoc sensitivty analysis of fecal indicator bacteria models to study scale. The vertical solid line and dotted lines indicate the intercept and 95% confidence intervals for the model that includes all values. Any intercept estimates outside of the full model confidence intervals implies the excluded sources are overly influential."
#| fig.height: 3
#| fig.width: 8 
#| out.width: "100%"
 tar_read(bac_scale, store = store)$p1
```

```{r tnscale}
#| fig.cap: "Post-hoc sensitivty analysis of total nitrogen models to study scale. The vertical solid line and dotted lines indicate the intercept and 95% confidence intervals for the model that includes all values. Any intercept estimates outside of the full model confidence intervals implies the excluded sources are overly influential."
#| fig.height: 3
#| fig.width: 8 
#| out.width: "100%"
 tar_read(tn_scale, store = store)$p1
```

```{r dinscale}
#| fig.cap: "Post-hoc sensitivty analysis of dissolved inorganic nitrogen models to study scale. The vertical solid line and dotted lines indicate the intercept and 95% confidence intervals for the model that includes all values. Any intercept estimates outside of the full model confidence intervals implies the excluded sources are overly influential."
#| fig.height: 3
#| fig.width: 8 
#| out.width: "100%"
 tar_read(tin_scale, store = store)$p1
```

```{r tpscale}
#| fig.cap: "Post-hoc sensitivty analysis of total phosphorus models to study scale. The vertical solid line and dotted lines indicate the intercept and 95% confidence intervals for the model that includes all values. Any intercept estimates outside of the full model confidence intervals implies the excluded sources are overly influential."
#| fig.height: 3
#| fig.width: 8 
#| out.width: "100%"
 tar_read(tp_scale, store = store)$p1
```

```{r po4scale}
#| fig.cap: "Post-hoc sensitivty analysis of orthophosphate models to study scale. The vertical solid line and dotted lines indicate the intercept and 95% confidence intervals for the model that includes all values. Any intercept estimates outside of the full model confidence intervals implies the excluded sources are overly influential."
#| fig.height: 3
#| fig.width: 8 
#| out.width: "100%"
 tar_read(po4_scale, store = store)$p1
```

```{r tssscale}
#| fig.cap: "Post-hoc sensitivty analysis of total suspended sediment models to study scale. The vertical solid line and dotted lines indicate the intercept and 95% confidence intervals for the model that includes all values. Any intercept estimates outside of the full model confidence intervals implies the excluded sources are overly influential."
#| fig.height: 3
#| fig.width: 8 
#| out.width: "100%"
 tar_read(tss_scale, store = store)$p1
```
